% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[overlapped]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=6.4in % increase textwidth to get smaller right margin
\sectionskip=0.2in
\usepackage{hyperref}
\usepackage[super]{nth}

\begin{document}

\name{Ebrahim M. Songhori\\[12pt]} % the\[12pt] adds a blank line after name

\address{
 \href{mailto:e.songhori@gmail.com }{e.songhori(at)gmail.com}\\
 \href{https://www.linkedin.com/in/esonghori/}{linkedin.com/in/esonghori/}\\
 \href{https://github.com/esonghori}{github.com/esonghori}
}

\begin{resume}

\section{Summary}
\begin{itemize}
\item {Experienced Software Engineer enthusiastic in machine learning engineering and research.}
\item {Experience in top industry research lab like {\bf Google DeepMind} and record of innovation and publications, e.g., \href{https://www.nature.com/articles/s41586-021-03544-w}{paper published at {\bf Nature}}.}
\item {Strong engineering professional skilled in Machine Learning, Reinforcement Learning, Ad Serving and Indexing.}
\end{itemize}
\section{Employment\\ Experiences}
\begin{itemize}
\item {\bf Senior Software Engineer at Google DeepMind}, Mountain View, CA\hfill 2019---
\begin{itemize}
\item{Member of Google DeepMind's Machine Learning for Systems team which applies modern machine learning techniques to optimize and improve computer systems.}
\end{itemize}
\item {\bf Software Engineer at Google Shopping Ads}, Mountain View, CA\hfill 2017--2019
\begin{itemize}
\item{Developed the infrastructure for a two-tower deep learning solution for low-latency and highly accurate ads retrieval in Google Shopping.}
\end{itemize}
\item {\bf Software Engineer Intern at Google}, Mountain View, CA\hfill Summer 2016\\
Developed an evaluation pipeline for retrieval using deep neural networks  for Google Shopping.
\item {\bf Software Engineer Intern at Google}, Mountain View, CA\hfill Summer 2015\\
Developed an intelligent monitoring and alerting system for Google Shopping Infrastructure.
\end{itemize}

\section{Technical\ Skills}
\begin{itemize}
\item {\bf Machine Learning}: Deep Learning, Deep Reinforcement Learning.
% \item Privacy-Preserving Computation: Multi-party Computation (MPC), Oblivious Transfer, Garbled Circuit (GC), Secret Sharing.  
\item {\bf Programming Skills:} Python, C/C++.
\item {\bf Other technologies:}
TensorFlow, Vizier, Protocol Buffer, Bigtable (NoSQL Database), MapReduce, Git, SQL, Amazon AWS.
\end{itemize}

\section{Education}
\begin{itemize}
\item {\bf Ph.D. in Electrical and Computer Engineering}\hfill  2015---2017\\
Rice University, TX.\\
Supervisor: Prof. Farinaz Koushanfar (University of California, San Diego)\\
Thesis Title: ``TinyGarble: Efficient, Scalable, and Versatile Privacy-Preserving Computation Through Sequential Garbled Circuit.''\\
Visitor student at University of California, San Diego, CA, 2015---2017. \\
An open-source and academic framework for privacy-preserving computation based on the Garbled Circuit protocol and hardware synthesis (available in \href{https://github.com/esonghori/TinyGarble}{TinyGarble Github}).
\item {\bf M.Sc. in Electrical and Computer Engineering}\hfill 2012---2014\\
Rice University, TX.
\item {\bf B.Sc. in Computer Engineering}\hfill 2007---2011\\
University of Tehran, Iran.
\end{itemize}

\section{Selected Publications and Patents}
\begin{itemize}
\item Mirhoseini, Azalia, Anna Goldie, Mustafa Yazgan, Joe Wenjie Jiang, {\bf Ebrahim Songhori}, Shen Wang, Young-Joon Lee et al. "A graph placement methodology for fast chip design." Nature 594, no. 7862 (2021): 207-212.
\item Goldie, Anna Darling, Azalia Mirhoseini, {\bf Ebrahim Songhori}, Wenjie Jiang, Shen Wang, Roger David Carpenter, Young-Joon Lee et al. "Generating integrated circuit placements using neural networks." U.S. Patent Application 17/555,085, filed April 7, 2022.
\item Zhang, Dan, Safeen Huda, {\bf Ebrahim Songhori}, Kartik Prabhu, Quoc Le, Anna Goldie, and Azalia Mirhoseini. "A full-stack search technique for domain optimized deep learning accelerators." In Proceedings of the 27th ACM ASPLOS, pp. 27-42. 2022.
% \item {\bf Songhori, Ebrahim M.}, M. Sadegh Riazi, Siam U. Hussain, Ahmad-Reza Sadeghi, and Farinaz Koushanfar. ``ARM2GC: Succinct Garbled Processor for Secure Computation.'' In Proceedings of the 56th Annual Design Automation Conference (DAC) 2019, pp. 1-6. 2019.
\item Riazi, M. Sadegh, Christian Weinert, Oleksandr Tkachenko, {\bf Ebrahim M. Songhori}, Thomas Schneider, and Farinaz Koushanfar. ``Chameleon: A hybrid secure computation framework for machine learning applications.'' In Proceedings of the 2018 on Asia Conference on Computer and Communications Security (ASIACCS), pp. 707-721. 2018.
% \item Riazi, M. Sadegh, {\bf Ebrahim M. Songhori}, and Farinaz Koushanfar. ``PriSearch: Efficient Search on Private Data.'' In Proceedings of the 54th Annual Design Automation Conference (DAC) 2017, p. 14. ACM, 2017.
% \item Mirhoseini, Azalia, Bita Darvish Rouhani, {\bf Ebrahim Songhori}, and Farinaz Koushanfar. ``ExtDict: Extensible Dictionaries for Data-and Platform-Aware Large-Scale Learning.'' In Parallel and Distributed Processing Symposium Workshops (ParLearning), 2017 IEEE International, IEEE, 2017; Won the best paper award.
% \item Mirhoseini, Azalia, Eva L. Dyer, {\bf Ebrahim M. Songhori}, Richard Baraniuk, and Farinaz Koushanfar. ``RankMap: A Framework for Distributed Learning From Dense Data Sets.'' IEEE Transactions on Neural Networks and Learning Systems (NNLS), 2017.
% \item Riazi, M. Sadegh, {\bf Ebrahim M. Songhori}, Ahmad-Reza Sadeghi, Thomas Schneider, and Farinaz Koushanfar. ``Toward Practical Secure Stable Matching.'' In Proceedings on Privacy Enhancing Technologies 2017, no. 1 (2017): 62-78.
% \item Rouhani, Bita Darvish, Azalia Mirhoseini, {\bf Ebrahim M. Songhori}, and Farinaz Koushanfar. ``Automated Real-Time Analysis of Streaming Big and Dense Data on Reconfigurable Platforms.'' ACM Transactions on Reconfigurable Technology and Systems (TRETS) 10, no. 1 (2016): 8.
% \item {\bf Songhori, Ebrahim M.}, Shaza Zeitouni, Ghada Dessouky, Thomas Schneider, Ahmad-Reza Sadeghi, and Farinaz Koushanfar. ``GarbledCPU: a MIPS processor for secure computation in hardware.'' In Proceedings of the 53rd Annual Design Automation Conference, p. 73. ACM, 2016.
% \item Mirhoseini, Azalia, Bita Darvish Rouhani, {\bf Ebrahim M. Songhori}, and Farinaz Koushanfar. ``Perform-ML: performance optimized machine learning by platform and content aware customization.'' In Proceedings of the 53rd Annual Design Automation Conference, p. 20. ACM, 2016.
% \item Mirhoseini, Azalia, Bita Darvish Rouhani, {\bf Ebrahim Songhori}, and Farinaz Koushanfar. ``Chime: Checkpointing long computations on intermittently energized IoT devices.'' In IEEE Transactions on Multi-Scale Computing Systems (TMSCS), p. 1. IEEE, 2016.
\item {\bf Songhori, Ebrahim M.}, Siam U. Hussain, Ahmad-Reza Sadeghi, Thomas Schneider, and Farinaz Koushanfar. ``TinyGarble: Highly compressed and scalable sequential garbled circuits.'' In Security and Privacy (SP), 2015 IEEE Symposium on, pp. 411-428. IEEE, 2015.
% \item {\bf Songhori, Ebrahim M.}, Siam U. Hussain, Ahmad-Reza Sadeghi, and Farinaz Koushanfar. ``Compacting privacy-preserving k-nearest neighbor search using logic synthesis.'' In Design Automation Conference (DAC), 2015 52nd ACM/EDAC/IEEE, pp. 1-6. IEEE, 2015.
% \item {\bf Songhori, Ebrahim M.}, Azalia Mirhoseini, Xuyang Lu, and Farinaz Koushanfar. ``AHEAD: automated framework for hardware accelerated iterative data analysis.'' In Proceedings of the 2015 Design, Automation \& Test in Europe Conference \& Exhibition (DATE), pp. 942-947. EDA Consortium, 2015.
% \item Rouhani, Bita Darvish, {\bf Ebrahim M. Songhori}, Azalia Mirhoseini, and Farinaz Koushanfar. ``SSketch: An Automated Framework for Streaming Sketch-based Analysis of Big Data on FPGA.'' In Field-Programmable Custom Computing Machines (FCCM), 2015 IEEE 23rd Annual International Symposium on, pp. 187-194. IEEE, 2015.
% \item Mirhoseini, Azalia, {\bf Ebrahim M. Songhori}, Bita Darvish Rouhani, and Farinaz Koushanfar.``Flexible Transformations For Learning Big Data.'' In Proceedings of the 2015 ACM SIGMETRICS International Conference on Measurement and Modeling of Computer Systems, pp. 453-454. ACM, 2015.
% \item Mirhoseini, Azalia, {\bf Ebrahim M. Songhori}, and Farinaz Koushanfar. ``Idetic: A high-level synthesis approach for enabling long computations on transiently-powered ASICs.'' In Pervasive Computing and Communications (PerCom), 2013 IEEE International Conference on, pp. 216-224. IEEE, 2013.
% \item Mirhoseini, Azalia, {\bf Ebrahim M. Songhori}, and Farinaz Koushanfar. ``Automated checkpointing for enabling intensive applications on energy harvesting devices.'' In Proceedings of the 2013 International Symposium on Low Power Electronics and Design, pp. 27-32. IEEE Press, 2013.
\end{itemize}

\section{Awards and\\ Honors}
\begin{itemize}
\item {\bf PhD Student Fellowship}, Houston, TX\hfill 2012\\
Rice University ECE Graduate Fellowship.
\item {\bf Valedictorian}, Tehran, Iran\hfill 2011\\
Ranked 1st in the class of 2011 Computer Engineering, University of Tehran.
\item {\bf Olympiad}, Tehran, Iran\\
Ranked 5th in the National Scientific Olympiads for College Students in Computer Engineering.\hfill 2009
Silver Medal in the National Scientific Olympiads for High School Students in Physics.\hfill 2006
\end{itemize}

% \section{Extracurricular\\ Activities}
% \begin{itemize}
% \item President, The Duncan Hall Fridge Room Club, Rice University, Houston, TX.\hfill 2013---2014
% \item Secretary, ACM Student Chapter, ECE, University of Tehran, Iran.\hfill 2009---2010
% \item Editor, ``88, The Reformist Students of University of Tehran'', the socio-political student publication, University of Tehran, Iran.\hfill 2008---2009
% \item Secretary of Public Relations, The Central Council of Student Association of Collage of Engineering, University of Tehran, Iran.\hfill 2009---2010
% \end{itemize}

\end{resume}
\end{document}